Networked Character Devices

### 2011-12-11 report/paper.tex
paper: udev subsection

>>>>

\lstinputlisting[
  lastline=1,
  caption={A simple \texttt{udev} rule for managing NCD device
  permissions.},
  label=lst:udevrule
]{udev.txt}

A lot of magic is performed on character devices in userspace by
\texttt{udev}. Currently we are using \texttt{udev} to manage the
permissions of imported devices (listing \ref{lst:udevrule}).

\lstinputlisting[
  firstline=3,
  caption={\texttt{udev} attributes required by userspace programs such
  as the \texttt{Xserver} for knowing a device is a keyboard.},
  label=lst:udevattr
]{udev.txt}

For more functionality, imported character devices must have certain
attributes such as those for the keyboard in listing \ref{lst:udevattr}.
Unfortunately setting them retroactively does not convince all programs
of a particular devices type. Therefore interfacing with specific kernel
subsystems such as \texttt{input} and \texttt{usb} will be required in
the future for enhanced functionality.
